---
title: "Dynamic Water Balance at MDV"
author: "Qing Zhan"
date: "19/07/2020"
output:
  word_document: default
  html_document: default
---

#### Reading data ####
```{r}

# dVol = Qin-Qout

require(lubridate)
library(readr)
require(dplyr)

setwd("C:\\Users\\QingZ\\PhD-Qing\\GitProject\\Mark_Dintel_Vliet_Project_Shared\\Modelling\\Waterbalance")# Set the working directory

#### Data preparation ####
# WL: Water depths
# Up: Upstream of sluice
# Down: Downstream of sluice

WL_Down_Vliet <- read_csv("WL_Down_Vliet.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
WL_Down_Dintel <- read_csv("WL_Down_Dintel.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(WL_Down_Vliet) <- c("Datum", "WL_Down_Vliet")
names(WL_Down_Dintel) <- c("Datum", "WL_Down_Dintel")
# Water depth measurements at downstream of Dintel and Vliet as indicator of Water depth dynamics in Volkerakmeer

WL_Up_Vliet <- read_csv("WL_Up_Vliet.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
WL_Up_Dintel <- read_csv("WL_Up_Dintel.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(WL_Up_Vliet) <- c("Datum", "WL_Up_Vliet")
names(WL_Up_Dintel) <- c("Datum", "WL_Up_Dintel")
# Water depth measurements at upstream of Dintel and Vliet as indicator of Water depth dynamics in Mark-Dintel-Vliet system

# Gastel (Molenbeak) water depth measurements
WL_Gastel <- read_csv("WL_Gastel.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(WL_Gastel) <- c("Datum", "WL_Gastel")

# Inflow discharges:
HF_Qin_MarkCanal <- read_csv("HF_Qin_MarkCanal.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(HF_Qin_MarkCanal) <- c("Datum","Qin_MarkCanal")

HF_Qin_Oranjeboombrug <- read_csv("HF_Qin_Oranjeboombrug.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(HF_Qin_Oranjeboombrug) <- c("Datum","Qin_Oranjeboombrug")

HF_Qin_BlauweKamer <- read_csv("HF_Qin_BlauweKamer.csv",
                               col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(HF_Qin_BlauweKamer) <- c("Datum","Qin_BlauweKamer")

HF_Qin_Molenbeak <- read_csv("HF_Qin_Molenbeak.csv",
                             col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(HF_Qin_Molenbeak) <- c("Datum","Qin_Molenbeak")

# Outflow discharges:
HF_Qout_Dintelsas <- read_csv("HF_Qout_Dintelsas.csv",
                              col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(HF_Qout_Dintelsas) <- c("Datum", "Qout_Dintelsas")

HF_Qout_Vliet <- read_csv("HF_Qout_Vliet.csv",
                          col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(HF_Qout_Vliet) <- c("Datum", "Qout_Vliet")

# Integrating dataset #
sTime_numeric <- seq(HF_Qin_MarkCanal$Datum[1]%>%as.numeric,HF_Qin_MarkCanal$Datum[length(HF_Qin_MarkCanal$Datum)]%>%as.numeric, by=3600) #hourly interval

WaterBudget_MDV <- data.frame(Datum = ymd_hms("1970-01-01 00:00:00")+sTime_numeric,WL_Down_Dintel=NA,WL_Down_Vliet=NA,WL_Up_Dintel=NA,WL_Up_Vliet=NA,WL_Gastel=NA,Qin_MarkCanal=NA,Qin_BlauweKamer=NA,Qin_Molenbeak=NA,Qin_Oranjeboombrug=NA,Qout_Dintelsas=NA,Qout_Vliet=NA)

WaterBudget_MDV$WL_Down_Dintel <- approx(WL_Down_Dintel$Datum%>%as.numeric,WL_Down_Dintel$WL_Down_Dintel,xout=WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$WL_Down_Vliet <- approx(WL_Down_Vliet$Datum%>%as.numeric,WL_Down_Vliet$WL_Down_Vliet,xout=WaterBudget_MDV$Datum%>%as.numeric)$y

WaterBudget_MDV$WL_Up_Dintel <- approx(WL_Up_Dintel$Datum%>%as.numeric,WL_Up_Dintel$WL_Up_Dintel,xout=WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$WL_Up_Vliet <- approx(WL_Up_Vliet$Datum%>%as.numeric,WL_Up_Vliet$WL_Up_Vliet,xout=WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$WL_Gastel <- approx(WL_Gastel$Datum%>%as.numeric,WL_Gastel$WL_Gastel, xout = WaterBudget_MDV$Datum%>%as.numeric)$y

WaterBudget_MDV$Qin_MarkCanal <- approx(HF_Qin_MarkCanal$Datum%>%as.numeric,HF_Qin_MarkCanal$Qin_MarkCanal,xout = WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$Qin_BlauweKamer <- approx(HF_Qin_MarkCanal$Datum%>%as.numeric,HF_Qin_MarkCanal$Qin_MarkCanal,xout = WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$Qin_Molenbeak <- approx(HF_Qin_Molenbeak$Datum%>%as.numeric,HF_Qin_Molenbeak$Qin_Molenbeak,xout = WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$Qin_Oranjeboombrug <- approx(HF_Qin_Oranjeboombrug$Datum%>%as.numeric,HF_Qin_Oranjeboombrug$Qin_Oranjeboombrug,xout = WaterBudget_MDV$Datum%>%as.numeric)$y

WaterBudget_MDV$Qout_Vliet <- approx(HF_Qout_Vliet$Datum%>%as.numeric,HF_Qout_Vliet$Qout_Vliet,xout = WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$Qout_Dintelsas <- approx(HF_Qout_Dintelsas$Datum%>%as.numeric,HF_Qout_Dintelsas$Qout_Dintelsas,xout = WaterBudget_MDV$Datum%>%as.numeric)$y

#### Compare the measurements at Dintel and Vliet downsteram as indicator of water depth dynamics at Volkerakmeer ####
plot(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Down_Dintel)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Down_Vliet, col=2)
plot(WaterBudget_MDV$WL_Down_Dintel, WaterBudget_MDV$WL_Down_Vliet)
lines(-2:2,-2:2,col=2) # 1:1 line

#### Compare depth measurements inside MDV system
plot(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Up_Dintel)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Up_Vliet, col=2)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Gastel,col=3)

#### Closing the water balance by adjusting the inflows at Gastel (Molenbeak)
Surface <- 50*(114-0)*40+50*(640-114)*50+50*(666-640)*100+50*(743-666)*40+50*(760-743)*26+50*(1117-760)*30 # m^2
WaterBudget_MDV$dt <- c(1, diff(as.numeric(WaterBudget_MDV$Datum))) # seconds
range(WaterBudget_MDV$dt)
WaterBudget_MDV <- WaterBudget_MDV[which(WaterBudget_MDV$dt!=0),]
#WaterBudget_MDV$dV <- c(0, diff(WaterBudget_MDV$WL_Up_Dintel))*Surface # m^3
WaterBudget_MDV$dV <- c(0, diff(WaterBudget_MDV$WL_Gastel))*Surface # m^3

#### Calculting the rest discharge to close the water budget ####
WaterBudget_MDV$Q_diff <- WaterBudget_MDV$dV/WaterBudget_MDV$dt # m3/s

#### Calculation of discharge at Gastel
WaterBudget_MDV$Q_Rest <- WaterBudget_MDV$Q_diff-(WaterBudget_MDV$Qin_MarkCanal+WaterBudget_MDV$Qin_BlauweKamer+WaterBudget_MDV$Qin_Oranjeboombrug-WaterBudget_MDV$Qout_Dintelsas-WaterBudget_MDV$Qout_Vliet)

#### Compare it with Measurements at Molenbeak ####
plot(WaterBudget_MDV$Datum,WaterBudget_MDV$Q_Rest, type = "l",ylim = c(-100,100))  
lines(WaterBudget_MDV$Datum,WaterBudget_MDV$Qin_Molenbeak, col=2)

```

#### Calculating the water level in Vliet based on Inflowsa and Outflows we have ####
```{r}

WaterBudget_MDV$dV_Cal = (WaterBudget_MDV$Qin_MarkCanal+WaterBudget_MDV$Qin_BlauweKamer+WaterBudget_MDV$Qin_Molenbeak+WaterBudget_MDV$Qin_Oranjeboombrug-WaterBudget_MDV$Qout_Dintelsas-WaterBudget_MDV$Qout_Vliet)*WaterBudget_MDV$dt

WaterBudget_MDV$WL_Cal = NA
WaterBudget_MDV$WL_Cal[1]=WaterBudget_MDV$WL_Up_Dintel[1]
for (t in 2:nrow(WaterBudget_MDV)) {
  WaterBudget_MDV$WL_Cal[t] = WaterBudget_MDV$WL_Cal[t-1]+WaterBudget_MDV$dV_Cal[t-1]/Surface
} 

plot(WaterBudget_MDV$Datum,WaterBudget_MDV$WL_Cal)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Up_Dintel, col=2)

legend("topright",legend = c("Calculation","Measurements"),col=1:2,text.col = 1:2,lty=1)

```

#### Correction of discharge at Gastel based on catchment area
```{r}

HF_Qin_Roosendaal_1 <- read_csv("HF_Qin_Roosendaal_1.csv",
                             col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
HF_Qin_Roosendaal_2 <- read_csv("HF_Qin_Roosendaal_2.csv",
                             col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))

names(HF_Qin_Roosendaal_1) <- c("Datum", "Qin_Roosendaal_1")
names(HF_Qin_Roosendaal_2) <- c("Datum", "Qin_Roosendaal_2")

plot(HF_Qin_Roosendaal_1$Datum, HF_Qin_Roosendaal_1$Qin_Roosendaal_1)
lines(HF_Qin_Roosendaal_2$Datum, HF_Qin_Roosendaal_2$Qin_Roosendaal_2, col=2)
HF_Qin_Roosendaal <- merge(HF_Qin_Roosendaal_1, HF_Qin_Roosendaal_2, by = "Datum")
plot(HF_Qin_Roosendaal$Qin_Roosendaal_1, HF_Qin_Roosendaal$Qin_Roosendaal_2)
lines(0:12,0:12, col="red")
plot(density(HF_Qin_Roosendaal$Qin_Roosendaal_2-HF_Qin_Roosendaal$Qin_Roosendaal_1))
# From the visualization Roosendaal_2 is on average larger than Roosendaal_1, from previous results that calculates water level dynamics based on inflow and outflow measurements, we had a underestimation of total Qin. Therefore, I'm going to use the Roosendaal_2 measurements rather than Roosendaal_1.

WaterBudget_MDV$Qin_Roosendaal <- approx(HF_Qin_Roosendaal$Datum%>%as.numeric, HF_Qin_Roosendaal$Qin_Roosendaal_2, xout = WaterBudget_MDV$Datum%>%as.numeric)$y

Roosendaal_CatchmentArea <- 2277 # 1 ha = 10000 m2
Molenbeek_CatchmentArea <- 1709 # 1 ha = 10000 m2

WaterBudget_MDV$Qin_Molenbeak_CorrectedByCatchment <- WaterBudget_MDV$Qin_Roosendaal/Roosendaal_CatchmentArea*Molenbeek_CatchmentArea

```

#### Calculation of Q_Polder with catchment area corrected Q_Gastel ####

```{r}
WaterBudget_MDV$Q_Polder <- WaterBudget_MDV$Q_Rest-WaterBudget_MDV$Qin_Molenbeak_CorrectedByCatchment

plot(WaterBudget_MDV$Datum,WaterBudget_MDV$Q_Rest, ylab = "Q_Polder (m3/s)", xlab = "",t="l")
lines(WaterBudget_MDV$Datum,WaterBudget_MDV$Q_Polder,col=2)
legend("topright",legend=c("Q_Gastel=0","Q_Gastel corrected for catchment area"),col=1:2,text.col = 1:2,lty=1)



plot(density(WaterBudget_MDV$Q_Rest-WaterBudget_MDV$Q_Polder,na.rm = T))

mean(WaterBudget_MDV$Q_Polder,na.rm = T)


```

```{r}
plot(WaterBudget_MDV$Datum, WaterBudget_MDV$Qin_MarkCanal)

mean(WaterBudget_MDV$Qin_MarkCanal)
```

#### Upstream Water depth dynamics ####
```{r}
setwd("C:\\Users\\QingZ\\PhD-Qing\\GitProject\\Mark_Dintel_Vliet_Project_Shared\\Modelling\\Waterbalance")
WL_Molenpolder_Bov <- read_csv("C:\\Users\\QingZ\\PhD-Qing\\GitProject\\Mark_Dintel_Vliet_Project_Shared\\Modelling\\Waterbalance\\WL_Molenpolder_Boven.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
WL_Molenpolder_Beneden <- read_csv("C:\\Users\\QingZ\\PhD-Qing\\GitProject\\Mark_Dintel_Vliet_Project_Shared\\Modelling\\Waterbalance\\WL_Molenpolder_Beneden.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))

Bov_Beneden_Molenpolder <- WL_Molenpolder_Bov$Waarde-WL_Molenpolder_Beneden$Waarde

plot(WL_Molenpolder_Beneden$Datum[which(month(WL_Molenpolder_Beneden$Datum)%in%(5:9))],Bov_Beneden_Molenpolder[which(month(WL_Molenpolder_Beneden$Datum)%in%(5:9))])

plot(density(Bov_Beneden_Molenpolder[which(month(WL_Molenpolder_Beneden$Datum)%in%(5:9))],na.rm = T))

plot(WL_Molenpolder_Beneden$Datum[which(month(WL_Molenpolder_Beneden$Datum)%in%c(1:4,10:12))],Bov_Beneden_Molenpolder[which(month(WL_Molenpolder_Beneden$Datum)%in%c(1:4,10:12))])

plot(density(Bov_Beneden_Molenpolder[which(month(WL_Molenpolder_Beneden$Datum)%in%c(1:4,10:12))],na.rm = T))



WL_Rooskendonk_Bov <- read_csv("C:\\Users\\QingZ\\PhD-Qing\\GitProject\\Mark_Dintel_Vliet_Project_Shared\\Modelling\\Waterbalance\\WL_Rooskensdonk_Boven.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(WL_Rooskendonk_Bov) <- c("Datum", "WL_Rooskendonk_Bov")

WL_Rooskendonk_Beneden <- read_csv("C:\\Users\\QingZ\\PhD-Qing\\GitProject\\Mark_Dintel_Vliet_Project_Shared\\Modelling\\Waterbalance\\WL_Rooskensdonk_Beneden.csv",col_types = cols(Datum = col_datetime(format = "%d-%m-%Y %H:%M:%S"), Eenheid = col_skip(),Serie = col_skip(), X5 = col_skip()))
names(WL_Rooskendonk_Beneden) <- c("Datum", "WL_Rooskendonk_Beneden")

WL_Rooskendonk <- merge(WL_Rooskendonk_Bov, WL_Rooskendonk_Beneden, by="Datum")

plot(WL_Rooskendonk$Datum, WL_Rooskendonk$WL_Rooskendonk_Bov-WL_Rooskendonk$WL_Rooskendonk_Beneden)
diff_Rooskendonk <- WL_Rooskendonk$WL_Rooskendonk_Bov-WL_Rooskendonk$WL_Rooskendonk_Beneden

plot(WL_Rooskendonk_Beneden$Datum[which(month(WL_Rooskendonk_Beneden$Datum)%in%(5:9))],diff_Rooskendonk[which(month(WL_Rooskendonk_Beneden$Datum)%in%(5:9))])

plot(density(diff_Rooskendonk[which(month(WL_Rooskendonk_Beneden$Datum)%in%(5:9))],na.rm = T))

plot(WL_Rooskendonk_Beneden$Datum[which(month(WL_Rooskendonk_Beneden$Datum)%in%c(1:4,10:12))],diff_Rooskendonk[which(month(WL_Rooskendonk_Beneden$Datum)%in%c(1:4,10:12))])

plot(density(diff_Rooskendonk[which(month(WL_Rooskendonk_Beneden$Datum)%in%c(1:4,10:12))],na.rm = T))

# Inclusion: Beneth is in the system

WaterBudget_MDV$WL_Molenpolder <- approx(WL_Molenpolder_Beneden$Datum%>%as.numeric,WL_Molenpolder_Beneden$Waarde,xout = WaterBudget_MDV$Datum%>%as.numeric)$y
WaterBudget_MDV$WL_Rooskendonk <- approx(WL_Rooskendonk_Beneden$Datum%>%as.numeric,WL_Rooskendonk_Beneden$WL_Rooskendonk_Beneden,xout = WaterBudget_MDV$Datum%>%as.numeric)$y
``` 

#### Comparison between upstream and downstream water level measurements ####
```{r}
#### Compare depth measurements inside MDV system
plot(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Up_Dintel)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Up_Vliet, col=2)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Gastel,col=3)

lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Molenpolder, col=4)
lines(WaterBudget_MDV$Datum, WaterBudget_MDV$WL_Rooskendonk, col=5)

# Dintel vs Molenpolder
plot(WaterBudget_MDV$WL_Down_Dintel, WaterBudget_MDV$WL_Molenpolder)
summary(lm(WaterBudget_MDV$WL_Molenpolder~WaterBudget_MDV$WL_Down_Dintel))

# Dintel vs Rooskendonk
plot(WaterBudget_MDV$WL_Down_Dintel, WaterBudget_MDV$WL_Rooskendonk)
summary(lm(WaterBudget_MDV$WL_Rooskendonk~WaterBudget_MDV$WL_Down_Dintel))

``` 


# Trunc  date to daily
```{r}
WaterBudget_MDV$Daily <- trunc(WaterBudget_MDV$Datum, "days")
WB_MDV_Day <- aggregate(WaterBudget_MDV[,2:21],by=list(as.character(WaterBudget_MDV$Daily)),mean)
names(WB_MDV_Day)[1] <- "Datum"
WB_MDV_Day$Datum <- ymd(WB_MDV_Day$Datum)

plot(WB_MDV_Day$Datum, WB_MDV_Day$Q_Polder,ylab = "Q_Polder (m3/s)", xlab = "")
plot(density(WB_MDV_Day$Q_Polder, na.rm = T),main = "density distribution of Q_Polder")

```

#### Water level fluctuations ####
```{r}

plot(WB_MDV_Day$Datum, WB_MDV_Day$WL_Up_Dintel, col=1, t="l")
lines(WB_MDV_Day$Datum, WB_MDV_Day$WL_Up_Vliet, col=2)

lines(WB_MDV_Day$Datum, WB_MDV_Day$WL_Gastel, col=3)

```

#### Water level fluctuations ####
```{r}
#### Closing the water balance by adjusting the inflows at Gastel (Molenbeak)
Surface <- 50*(114-0)*40+50*(640-114)*50+50*(666-640)*100+50*(743-666)*40+50*(760-743)*26+50*(1117-760)*30 # m^2
WB_MDV_Day$dt <- c(1, diff(as.numeric(WB_MDV_Day$Datum))) # seconds
range(WB_MDV_Day$dt)
WB_MDV_Day <- WB_MDV_Day[which(WB_MDV_Day$dt!=0),]
#WB_MDV_Day$dV <- c(0, diff(WB_MDV_Day$WL_Up_Dintel))*Surface # m^3
WB_MDV_Day$dV <- c(0, diff(WB_MDV_Day$WL_Gastel))*Surface # m^3

#### Calculting the rest discharge to close the water budget ####
WB_MDV_Day$Q_diff <- WB_MDV_Day$dV/(WB_MDV_Day$dt*86400) # m3/s

#### Calculation of discharge at Gastel
WB_MDV_Day$Q_Rest <- WB_MDV_Day$Q_diff-(WB_MDV_Day$Qin_MarkCanal+WB_MDV_Day$Qin_BlauweKamer+WB_MDV_Day$Qin_Oranjeboombrug-WB_MDV_Day$Qout_Dintelsas-WB_MDV_Day$Qout_Vliet)

#### Compare it with Measurements at Molenbeak ####
plot(WB_MDV_Day$Datum,WB_MDV_Day$Q_Rest, type = "l",ylim = c(-100,100))  
lines(WB_MDV_Day$Datum,WB_MDV_Day$Qin_Molenbeak, col=2)
```

#### Q vs delta water depth
```{r}

WaterBudget_MDV$Dintel_diff_WaterDepth <- WaterBudget_MDV$WL_Up_Dintel-WaterBudget_MDV$WL_Down_Dintel
WaterBudget_MDV$Vliet_diff_WaterDepth <- WaterBudget_MDV$WL_Gastel-WaterBudget_MDV$WL_Down_Vliet

plot(WaterBudget_MDV$Dintel_diff_WaterDepth, WaterBudget_MDV$Qout_Dintelsas,ylab = "discharge at Dintelsas", xlab = "delta water depth (upstream - downstream)")
summary(lm(WaterBudget_MDV$Qout_Dintelsas~WaterBudget_MDV$Dintel_diff_WaterDepth))

plot(WaterBudget_MDV$Vliet_diff_WaterDepth,WaterBudget_MDV$Qout_Vliet)
summary(lm(WaterBudget_MDV$Qout_Vliet~WaterBudget_MDV$Vliet_diff_WaterDepth))
```

#### Q_Polder daily data
```{r}

WB_MDV_Day$Q_Polder <- WB_MDV_Day$Q_Rest-WB_MDV_Day$Qin_Molenbeak_CorrectedByCatchment

plot(WB_MDV_Day$Datum,WB_MDV_Day$Q_Rest, ylab = "Q_Polder (m3/s)", xlab = "",t="l", ylim = c(-20, 100))
lines(WB_MDV_Day$Datum,WB_MDV_Day$Q_Polder,col=2)
legend("topright",legend=c("Q_Gastel=0","Q_Gastel corrected for catchment area"),col=1:2,text.col = 1:2,lty=1,cex=0.8)



plot(density(WB_MDV_Day$Q_Rest-WB_MDV_Day$Q_Polder,na.rm = T),main = "density distribution of Q_Polder")

mean(WB_MDV_Day$Q_Polder,na.rm = T)

# for polder discharge in summer
plot(WB_MDV_Day$Datum[which(month(WB_MDV_Day$Datum)%in%c(5:9))],WB_MDV_Day$Q_Polder[which(month(WB_MDV_Day$Datum)%in%c(5:9))], xlab = "",ylab = "Q_Polder in summer",t="p",col=1,pch=19)
mean(WB_MDV_Day$Q_Polder[which(month(WB_MDV_Day$Datum)%in%c(5:9))])

points(WB_MDV_Day$Datum[which(month(WB_MDV_Day$Datum)%in%c(10,11,12,1,2,3,4))],WB_MDV_Day$Q_Polder[which(month(WB_MDV_Day$Datum)%in%c(10,11,12,1,2,3,4))],col=2,pch=19)
legend("topright",legend=c("summer","no summer"),col=1:2,text.col = 1:2,pch=19,cex=0.8)

mean(WB_MDV_Day$Q_Polder[which(month(WB_MDV_Day$Datum)%in%c(10,11,12,1,2,3,4))],na.rm = T)
```

#### Q vs delta Water depth ####
```{r}

WB_MDV_Day$Dintel_diff_WaterDepth <- WB_MDV_Day$WL_Up_Dintel-WB_MDV_Day$WL_Down_Dintel
WB_MDV_Day$Vliet_diff_WaterDepth <- WB_MDV_Day$WL_Gastel-WB_MDV_Day$WL_Down_Vliet

plot(WB_MDV_Day$Dintel_diff_WaterDepth, WB_MDV_Day$Qout_Dintelsas,ylab = "discharge at Dintelsas", xlab = "delta water depth (upstream - downstream)")
summary(lm(WB_MDV_Day$Qout_Dintelsas~WB_MDV_Day$Dintel_diff_WaterDepth))

plot(WB_MDV_Day$Vliet_diff_WaterDepth,WB_MDV_Day$Qout_Vliet)
summary(lm(WB_MDV_Day$Qout_Vliet~WB_MDV_Day$Vliet_diff_WaterDepth))
```
